00_datawrangling.Rmd

### 2019-04-23 analysis/00_datawrangling.Rmd
better files

```{r setup, include=FALSE}
# https://bioconductor.org/packages/release/bioc/vignettes/DESeq2/inst/doc/DESeq2.html
library(tidyverse)
```

@@

write.csv(geneinfo, "../results/00_geneinfo.csv", row.names = TRUE)
```

>>>>

```{r setup}
# https://bioconductor.org/packages/release/bioc/vignettes/DESeq2/inst/doc/DESeq2.html
library(tidyverse)
```

@@

write.csv(geneinfo, "../metadata/00_geneinfo.csv", row.names = TRUE)
```
